SUPPLEMENTARY INFORMATION FOR\\ NMRlipids III: Lipid--Cholesterol Interactions in Atomistic Resolution Molecular Dynamics Simulations

### 2023-05-03 MANUSCRIPT/manuscript.tex
Update

\author{Fernando Favela-Rosales}
\affiliation{Departamento de F\'isica, Centro de Investigaci\'on y de Estudios Avanzados del IPN, Apartado Postal 14-740, 07000 M\'exico D.F., M\'exico}
%
\author{Peter Heftberger}
\affiliation{Institute of Molecular Biosciences, Biophysics Division, NAWI Graz, University of Graz, AT-8010 Graz, Austria}
%
\author{Matti Javanainen}
\affiliation{Institute of Organic Chemistry and Biochemistry, Academy of Sciences of the Czech Republic, CZ-16000 Prague 6, Czech Republic}
\alsoaffiliation{Institute of Biotechnology, University of Helsinki, FI-00790 Helsinki, Finland}
\email{matti.javanainen@helsinki.fi}
%
\author{Jesper J. Madsen}
\affiliation{Department of Global Health, College of Public Health}
\alsoaffiliation{University of South Florida}
%
\author{Josef Melcr}
\affiliation{Institute of Organic Chemistry and Biochemistry, Academy of Sciences of the Czech Republic, CZ-16000 Prague 6, Czech Republic}
%
\author{Markus Miettinen}
\affiliation{Department of Chemistry, University of Bergen, Norway}
\alsoaffiliation{Computational Biology Unit, Department of Informatics, University of Bergen, NO-5008 Bergen, Norway}
%
\author{O. H. Samuli Ollila}
\affiliation{Institute of Organic Chemistry and Biochemistry, Academy of Sciences of the Czech Republic, CZ-16000 Prague 6, Czech Republic}
\alsoaffiliation{Institute of Biotechnology, University of Helsinki, FI-00790 Helsinki, Finland}
\email{samuli.ollila@helsinki.fi}
%
\author{Georg Pabst}
\affiliation{Institute of Molecular Biosciences, Biophysics Division, NAWI Graz, University of Graz, AT-8010 Graz, Austria}
\alsoaffiliation{BioTechMed-Graz, Graz 8010, Austria}
%
\author{Thomas Piggot}
\affiliation{School of Chemistry, University of Southampton, Southampton SO17 1BJ, United Kingdom}
\alsoaffiliation{Chemical Biological and Radiological Sciences, Defence Science and Technology Laboratory, Porton Down, Salisbury, Wiltshire SP4 0JQ, United Kingdom}

>>>>

\author{Peter Heftberger}
\affiliation{Institute of Molecular Biosciences, Biophysics Division, NAWI Graz, University of Graz, AT-8010 Graz, Austria}
%
\author{Matti Javanainen}
\affiliation{Institute of Organic Chemistry and Biochemistry, Academy of Sciences of the Czech Republic, CZ-16000 Prague 6, Czech Republic}
\alsoaffiliation{Institute of Biotechnology, University of Helsinki, FI-00790 Helsinki, Finland}
\email{matti.javanainen@helsinki.fi}
%
\author{Jesper J. Madsen}
\affiliation{Department of Global Health, College of Public Health}
\alsoaffiliation{University of South Florida}
%
\author{Josef Melcr}
\affiliation{Institute of Organic Chemistry and Biochemistry, Academy of Sciences of the Czech Republic, CZ-16000 Prague 6, Czech Republic}
%
\author{Markus Miettinen}
\affiliation{Department of Chemistry, University of Bergen, Norway}
\alsoaffiliation{Computational Biology Unit, Department of Informatics, University of Bergen, NO-5008 Bergen, Norway}
%
\author{O. H. Samuli Ollila}
\affiliation{Institute of Organic Chemistry and Biochemistry, Academy of Sciences of the Czech Republic, CZ-16000 Prague 6, Czech Republic}
\alsoaffiliation{Institute of Biotechnology, University of Helsinki, FI-00790 Helsinki, Finland}
\email{samuli.ollila@helsinki.fi}
%
\author{Georg Pabst}
\affiliation{Institute of Molecular Biosciences, Biophysics Division, NAWI Graz, University of Graz, AT-8010 Graz, Austria}
\alsoaffiliation{BioTechMed-Graz, Graz 8010, Austria}
%

### 2023-05-03 MANUSCRIPT/manuscriptSUPPL.tex
Update

\author{Fernando Favela-Rosales}
\affiliation{Departamento de F\'isica, Centro de Investigaci\'on y de Estudios Avanzados del IPN, Apartado Postal 14-740, 07000 M\'exico D.F., M\'exico}
%
\author{Peter Heftberger}
\affiliation{Institute of Molecular Biosciences, Biophysics Division, NAWI Graz, University of Graz, Graz 8010, Austria}
%
\author{Matti Javanainen}
\affiliation{Institute of Organic Chemistry and Biochemistry,
Academy of Sciences of the Czech Republic, 
Prague 6, Czech Republic}
\alsoaffiliation{Institute of Biotechnology, University of Helsinki}
\email{matti.javanainen@helsinki.fi}
%
\author{Jesper J. Madsen}
\affiliation{Department of Global Health, College of Public Health}
\alsoaffiliation{University of South Florida}
%
\author{Josef Melcr}
\affiliation{Institute of Organic Chemistry and Biochemistry,
Academy of Sciences of the Czech Republic, 
Prague 6, Czech Republic}
%
\author{Markus Miettinen}
\affiliation{Department of Chemistry, University of Bergen, Norway}
\alsoaffiliation{Computational Biology Unit, Department of Informatics, University of Bergen, Norway}

%
\author{O. H. Samuli Ollila}
\affiliation{Institute of Organic Chemistry and Biochemistry,
Academy of Sciences of the Czech Republic, 
Prague 6, Czech Republic}
\alsoaffiliation{Institute of Biotechnology, University of Helsinki}
\email{samuli.ollila@helsinki.fi}
%
\author{Georg Pabst}
\affiliation{Institute of Molecular Biosciences, Biophysics Division, NAWI Graz, University of Graz, Graz 8010, Austria}
\alsoaffiliation{BioTechMed-Graz, Graz 8010, Austria}
%
\author{Thomas Piggot}
\affiliation{School of Chemistry, University of Southamptaon, Southampton SO17 1BJ, United Kingdom}
\alsoaffiliation{Chemical Biological and Radiological Sciences, Defence Science and Technology Laboratory, Porton Down, Salisbury, Wiltshire SP4 0JQ, United Kingdom}

>>>>

\author{Peter Heftberger}
\affiliation{Institute of Molecular Biosciences, Biophysics Division, NAWI Graz, University of Graz, Graz 8010, Austria}
%
\author{Matti Javanainen}
\affiliation{Institute of Organic Chemistry and Biochemistry,
Academy of Sciences of the Czech Republic, 
Prague 6, Czech Republic}
\alsoaffiliation{Institute of Biotechnology, University of Helsinki}
\email{matti.javanainen@helsinki.fi}
%
\author{Jesper J. Madsen}
\affiliation{Department of Global Health, College of Public Health}
\alsoaffiliation{University of South Florida}
%
\author{Josef Melcr}
\affiliation{Institute of Organic Chemistry and Biochemistry,
Academy of Sciences of the Czech Republic, 
Prague 6, Czech Republic}
%
\author{Markus Miettinen}
\affiliation{Department of Chemistry, University of Bergen, Norway}
\alsoaffiliation{Computational Biology Unit, Department of Informatics, University of Bergen, Norway}

%
\author{O. H. Samuli Ollila}
\affiliation{Institute of Organic Chemistry and Biochemistry,
Academy of Sciences of the Czech Republic, 
Prague 6, Czech Republic}
\alsoaffiliation{Institute of Biotechnology, University of Helsinki}
\email{samuli.ollila@helsinki.fi}
%
\author{Georg Pabst}
\affiliation{Institute of Molecular Biosciences, Biophysics Division, NAWI Graz, University of Graz, Graz 8010, Austria}
\alsoaffiliation{BioTechMed-Graz, Graz 8010, Austria}
%
